\documentclass[11pt]{article}
\usepackage[paperwidth=8.5in, paperheight=5.5in]{geometry}
\usepackage{amsfonts}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{graphicx}
\usepackage{asymptote}
\usepackage{multicol}

%my inputs
\usepackage{framed}
\newtheorem*{definition}{Definition}

\makeatletter
\def\thm@space@setup{%
  \thm@preskip=\parskip \thm@postskip=0pt
}
\makeatother
\theoremstyle{definition}
\newtheorem{problem}{Problem}
\newtheorem*{solution}{Solution}
\newtheorem*{answer}{Answer}
\newtheorem*{solution1}{Solution 1}
\newtheorem*{solution2}{Solution 2}

\def\st{^{\scriptstyle\mbox{st}}}
\def\nd{^{\scriptstyle\mbox{nd}}}
\def\rd{^{\scriptstyle\mbox{rd}}}
\def\th{^{\scriptstyle\mbox{th}}}

\usepackage{fancyhdr}
\pagestyle{fancy}
\cfoot{}
\lhead{\logo}
\rhead{\righthead\vspace{-1em}}
\rfoot{\emph{\sevenpoints}}
\setlength{\headheight}{13em} %previously 16em
\setlength{\headsep}{2em}
\setlength{\voffset}{-1in}
\setlength{\hoffset}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\textheight}{0.25in}
\newlength\FHoffset\setlength\FHoffset{0.5in}
\addtolength\headwidth{2\FHoffset}
\fancyheadoffset{\FHoffset}
\newlength\FHleft\setlength\FHleft{0in}
\newlength\FHright\setlength\FHright{-1in}
\newbox\FHline\setbox\FHline=\hbox{\hsize=\paperwidth%
  \hspace*{\FHleft}%
  \rule{\dimexpr\headwidth-\FHleft-\FHright\relax}{\headrulewidth}\hspace*{\FHright}%
}
\renewcommand\headrule{\vskip-.7\baselineskip\copy\FHline}
\newcommand{\olyinfo}[1]{\begin{flushright} \itshape #1 \end{flushright}\medskip}
\newcommand{\nmbox}[1]{\fbox{\sffamily\LARGE\vphantom y#1} \par\vspace{1em}} % normal box
\newcommand{\fdbox}[2]{\fbox{\sffamily\LARGE\vphantom y#1: \bfseries #2} \par\vspace{1em}} % field box


\begin{document}

\newcommand{\logo}{%
\begin{minipage}[b]{22em}
\centering\noindent
%{\huge\sffamily Intermediate Math Open}
\\[0.5em]
\begin{minipage}[t][4em][t]{12em} \centering
{\huge \bfseries ${\bf 26^{\text{th}}}$ TJIMO } \\
\textsc{\large Alexandria, Virginia}
\end{minipage}
\end{minipage}
\vspace*{-0.05em}
}
\newcommand{\sevenpoints}{}
\newcommand{\righthead}{\fdbox{Round}{Practice Guts}}


\section*{Set 1}
\begin{enumerate}

\item How many even primes are divisible by 3?
\item Find the sum of the number of edges and number of vertices of a cube.
\item Bill flips 4 coins. How many possible outcomes are there? (For example, one outcome is HHTH.)
\item Sarah has a string of length 10, and makes a circle out of it. What is the radius of the circle? Express your answer in terms of $\pi$.

\end{enumerate}

\eject

\section*{Set 2}
\begin{enumerate}
\setcounter{enumi}{4}
\item Find the area of an equilateral triangle with side length 2.
\item If the function $f(x) = 2x^2 - 1$ and $g(x) = x + 2$, find $f(g(3))$.
\item A trapezoid has 2 right angles. Its legs have lengths 4 and 5, and the shorter of the other two sides has length 4. Find its area.
\item Find the probability that when two fair, six-sided dice are rolled, their sum is greater than 9.
\end{enumerate}

\eject

\section*{Set 3}
\begin{enumerate}
\setcounter{enumi}{8}
\item If $\frac{x(D+8)}{2} = 4x + 16$, find the value of $xD$.
\item If 10 coins are tossed, what is the probability that there are exactly 7 heads?
\item Evaluate $1-2+3-4+\dotsb+99-100$.
\item Rabin Karp is trying to find 2 identical strings. He randomly draws strings from a collection of 100 different pairs of strings. How many strings must he draw until he is sure that he has at least one matching pair?
\end{enumerate}

\end{document}
